Secure Composition of Robust and Optimising Compilers

### 2025-02-06 icfp/sections/intro.tex
Intro

As of today, there exist a number of programming languages that enforce security-relevant properties.
One of the most used programming languages in that space is Rust~\cite{}, which guarantees basic memory safety.
That is, there is a guarantee that all memory accesses are {\em temporally} as well as {\em spatially} safe. 
Temporal memory safety is the absence of use-after-free and use-after-reallocation bugs and necessitates tracking of pointer provenance\footnote{Due to potential use-after-reallocation bugs.}. %TODO: example?
Provenance of pointers is also crucial information, together with bounds, for spatial memory safety, which ensures that all accesses are within bounds of an allocated object.

>>>>

As of today, there exist a number of programming languages that enforce security-relevant properties.
One of the most used programming languages in that space is Rust~\cite{}, which guarantees basic memory safety.
That is, there is a guarantee that all memory accesses are {\em temporally} as well as {\em spatially} safe. 
Temporal memory safety is the absence of use-after-free and use-after-reallocation bugs and necessitates tracking of pointer provenance\footnote{Due to potential use-after-reallocation bugs.}. %TODO: example?
Provenance of pointers is also crucial information, together with bounds, for spatial memory safety, which ensures that all accesses are within bounds of an allocated object.
There is a large body of prior work modifying existing memory-unsafe languages~\cite{} or providing compiler-level enforcements~\cite{} for both temporal and spatial memory safety.
Moreover, modern processors can speculatively load memory which has become the source of bugs not fixable by temporal or spatial memory safety.
Here, other mechanisms~\cite{} are necessary in order to enforce privacy of data.
